---
title: "Project title"
subtitle: "Proposal"
format: html
editor: visual
---

```{r}
#| label: load-pkgs
#| message: false

library(tidyverse)
```

# Data 1

## Introduction and data

-   Identify the source of the data.

The source of the data is FiveThirtyEight, a statistics-centered news source.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

Researchers at FiveThirtyEight have been quantifying the soccer teams' past performances, and then collecting data on the results of each matches. The data originally started being collected in 2019.

-   Write a brief description of the observations.

The observations are individual matches from all club soccer matches since 2022, with the exception of the Chinese Super League's 2019 season. The columns describe FiveThirtyEight's predictions for each match and then the result of the match. FiveThirtyEight uses their SPI model as predictions, then the data set included expected goals and goals scored for each team.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    1.  How accurately does FiveThirtyEight's projected goals scored predict actual goals scored depending on league?

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

My research topic relates how well FiveThirtyEight can predict the results of each match in each league. In short, I'm looking for which leagues are the most and least predictable. If FiveThirtyEight's predictions are consistently accurate for a league, that league could be considered relatively predictable. To quantify the results, I'm planning on using projected goals scored with actual goals scored. My hypotheses is that higher quality leagues, such as the English Premier League, La Liga, and the UEFA Champions League are the most predictable as those leagues have the largest discrepancies of talent based on club.

-   Identify the types of variables in your research question. Categorical? Quantitative?

Categorical variables include: League, Team1, and Team2

Quantitative variables include: Date, League ID, spi1, spi2, prob1, prob2, probtie, importance1, importance2, score1, score2, xg1, xg2, nsxg1, nsxg2, adj_score1, adj_score2

## Literature

-   Find one published credible article on the topic you are interested in researching.

**Anzer G and Bauer P (2021) A Goal Scoring Probability Model for Shots Based on Synchronized Positional and Event Data in Football (Soccer). Front. Sports Act. Living 3:624475. doi: 10.3389/fspor.2021.624475 https://www.frontiersin.org/articles/10.3389/fspor.2021.624475/full**

-   Provide a one paragraph summary about the article.

**This article describes how, because goals are often used as an evualitive measure for quality of teams and players, researches wanted to create a prediction model that could calculate the quality of the goal. The expected goals model (xG) discussed in the paper is "validated statistically and with professional match analysts"; it uses a gradient boosting algorithm with synchronized positional and event data from 105, 627 shots taken in the German soccer league (the Bundesliga). The overall study, and use of this specific prediction model, allows for the better assessment of teams' and players' quality of performance.**

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

**Where this article explains the ins and outs of using mathematical modeling in order to predict the quality of goals in professional soccer, our project proposes to investigate the efficacy of prediction models for the number of goals scored per league**

## Glimpse of data

```{r}
#| label: load-data-1

spi_matches_latest = read.csv("data/spi_matches_latest.csv")
glimpse(spi_matches_latest)
```

# Data 2

## Introduction and data

-   Identify the source of the data.

    -   The source is the US department of education's website on Equity in Athletics

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    -   Each University was asked to submit the data to the US department of education via a form. The DOE then compiles this information.

-   Write a brief description of the observations.

    -   The data gives basic information such as the name of the school, location, NCAA division, funding allocations, as well as the expenses by sports.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    -   To what extent can college athletics' recruitment funds be predicted by the level of athletic scholarships provided to student athletes?

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    -   The data provides us with the ratio of student aid (Male:Female) as well as the funding provided for recruitment of these individuals. We will be looking to see how accurately we can use this ratio to predict the recruitment budgets. We will separate this by state in order to account for regional biases that may interfere with these predictions. We predict that the ratio will, to a high degree, predict the recruitment funding as, schools willing to put money into students' financial aid will be willing to put money into their recruitment.

-   Identify the types of variables in your research question. Categorical? Quantitative?

    -   Both the ratios and budgets are quantative, States are a categorical variable.

## Literature

-   Find one published credible article on the topic you are interested in researching.

**https://www.seattletimes.com/sports/ncaa-title-ix-report-spending-up-gender-gaps-remain/**

**Meredith, L. (2017, June 21). NCAA Title IX Report: Spending up, gender gaps remain. The Seattle Times.**

-   Provide a one paragraph summary about the article.

**The article clearly outlines the inequities between men's and women's NCAA sports budgeting. Across all divisions of NCAA sports, the funding for both men's and women's sports has doubled over the past decade. However, the largest gap can be observed in division 1 sports. On average, Universities spend, approximately, double on their men's teams than they do on their women's teams. It is important to note, however, that this is largely skewed by the schools with football teams (although that is most). Schools without football teams spend almost the same (\$5 million each). The gap is largest in schools with top tier football teams. Taking that facotr into account, in 1015, schools spent an estimated \$27.3 million on men's sports and about \$10.5 million on their women's teams**

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

**Our project builds upon the information provided in the article because, it not only adds the differentiating factor of states, but it builds on the idea of the gender gap in recruitment budgets by attempting to create a model that can predict such gaps based upon the allocation of aid towards each gender of athlete.**

## Glimpse of data

```{r}
#| label: load-data-2

EADA_2021 = read.csv("data/Copy of EADA_2021.csv")


eada <- EADA_2021[,-27:-4274]
glimpse(eada)
  
```

# Data 3

## Introduction and data

-   Identify the source of the data.

    The data is sourced from the Collective Learning group at the MIT Media Lab.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    The data was collected in 2013 from biographies of famous people on Wikipedia, written in more than 25 languages.

-   Write a brief description of the observations.

    Each observation represents a webpage on Wikipedia that contains the biography of a specific famous person. The variables recorded for each observation include the location of that person's birth, as well as their gender and occupation. Data about the popularity of each page is also included, such as the number of languages the page has been translated into, the number of times the page has been viewed, and a measure called the Historical Popularity Index (HPI) that is derived from the number of different-language pages, the time since the person's birth, and page views, to reflect a person's popularity over time.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    Does the particular industry a person worked in have an influence on their overall popularity?

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    The research topic will focus on the relationship industry has with both HPI and the number of languages the page has been translated into. We will look at the values for HPI and number of languages for each industry in the dataset to assess popularity across multiple countries. We predict that more publicly influential industries such as Government and Film will be correlated with higher HPI and a greater number of translations.

-   Identify the types of variables in your research question. Categorical? Quantitative?

    Industry is a categorical variable, while HPI and number of languages are quantitative variables.

## Literature

-   Find one published credible article on the topic you are interested in researching.

    **https://www.statista.com/statistics/421169/most-followers-instagram/**

-   Provide a one paragraph summary about the article.

    **This is not an article, so much as a published summary of the individuals on instagram with the most followers as of January 2023. In millions, it displays the top ten most followed people: 1) Cristiano Ronaldo (539M); 2) Lionel Messi (424M); 3) Kylie Jenner (379M); 4) Selena Gomez (373M); 5)Dwayne Johnson (360M); 6) Ariana Grande (352M); 7) Kim Kardashian (342M); 8) Beyonce (292M); 9) Khloe Kardashian (291M); 10) Justin Bieber (274M). What can be deduced from this data is that, on instagram, the top two most followed people are athletes, specifically soccer. The rest of the top ten individuals are either influencers or singers who *also* have an assortment of cosmetics and/or clothing brands.**

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

    **Our project would build upon the article above by focusing on the popularity of any given industry, as measured by the number of languages a Wikipedia page has been translated to.**

## Glimpse of data

```{r}
#| label: load-data-3

pantheon = read.csv("data/pantheon.csv")
glimpse(pantheon)
```
