---
title: "Project title"
subtitle: "Proposal"
format: html
editor: visual
---

```{r}
#| label: load-pkgs
#| message: false

library(tidyverse)
```

# Data 1

## Introduction and data

-   Identify the source of the data.

The source of the data is FiveThirtyEight, a statistics-centered news source.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

Researchers at FiveThirtyEight have been quantifying the soccer teams' past performances, and then collecting data on the results of each matches. The data originally started being collected in 2019.

-   Write a brief description of the observations.

The observations are individual matches from all club soccer matches since 2022, with the exception of the Chinese Super League's 2019 season. The columns describe FiveThirtyEight's predictions for each match and then the result of the match. FiveThirtyEight uses their SPI model as predictions, then the data set included expected goals and goals scored for each team.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    1.  How accurately does FiveThirtyEight's projected goals scored predict actual goals scored depending on league?

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

My research topic relates how well FiveThirtyEight can predict the results of each match in each league. In short, I'm looking for which leagues are the most and least predictable. If FiveThirtyEight's predictions are consistently accurate for a league, that league could be considered relatively predictable. To quantify the results, I'm planning on using projected goals scored with actual goals scored. My hypotheses is that higher quality leagues, such as the English Premier League, La Liga, and the UEFA Champions League are the most predictable as those leagues have the largest discrepancies of talent based on club.

-   Identify the types of variables in your research question. Categorical? Quantitative?

Categorical variables include: League, Team1, and Team2

Quantitative variables include: Date, League ID, spi1, spi2, prob1, prob2, probtie, importance1, importance2, score1, score2, xg1, xg2, nsxg1, nsxg2, adj_score1, adj_score2

## Literature

-   Find one published credible article on the topic you are interested in researching.

-   Provide a one paragraph summary about the article.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

## Glimpse of data

```{r}
#| label: load-data-1

spi_matches_latest = read.csv("data/spi_matches_latest.csv")
glimpse(spi_matches_latest)
```

# Data 2

## Introduction and data

-   Identify the source of the data.

    -   The source is the US department of education's website on Equity in Athletics

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

    -   Each University was asked to submit the data to the US department of education via a form. The DOE then compiles this information.

-   Write a brief description of the observations.

    -   The data gives basic information such as the name of the school, location, NCAA division, funding allocations, as well as the expenses by sports.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

    -   How accurately can student aid Male to Female ratio predict funding allocations across all sports recruitment budgets based on state.

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

    -   The data provides us with the ratio of student aid (Male:Female) as well as the funding provided for recruitment of these individuals. We will be looking to see how accurately we can use this ratio to predict the recruitment budgets. We will separate this by state in order to account for regional biases that may interfere with these predictions. We predict that the ratio will, to a high degree, predict the recruitment funding as, schools willing to put money into students' financial aid will be willing to put money into their recruitment.

-   Identify the types of variables in your research question. Categorical? Quantitative?

    -   Both the ratios and budgets are quantative, States are a categorical variable.

## Literature

-   Find one published credible article on the topic you are interested in researching.

-   Provide a one paragraph summary about the article.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

## Glimpse of data

```{r}
#| label: load-data-2

EADA_2021 = read.csv("data/Copy of EADA_2021.csv")
glimpse(EADA_2021)
```

# Data 3

## Introduction and data

-   Identify the source of the data.

-   State when and how it was originally collected (by the original data curator, not necessarily how you found the data).

-   Write a brief description of the observations.

## Research question

-   A well formulated research question. (You may include more than one research question if you want to receive feedback on different ideas for your project. However, one per data set is required.)

-   A description of the research topic along with a concise statement of your hypotheses on this topic.

-   Identify the types of variables in your research question. Categorical? Quantitative?

## Literature

-   Find one published credible article on the topic you are interested in researching.

-   Provide a one paragraph summary about the article.

-   In 1-2 sentences, explain how your research question builds on / is different than the article you have cited.

## Glimpse of data

```{r}
#| label: load-data-3

# add code here
```
