---
title: "Project title"
subtitle: "Report"
format: html
editor: visual
execute:
  echo: true
---

```{r}
#| label: load-pkgs


library(tidyverse)
```

```{r}
#| label: load-data

EADA_2021 = read.csv("data/Copy of EADA_2021.csv")


eada <- EADA_2021[,-27:-4274]
glimpse(eada)
```

**Introduction**

Duke University is intrinsically connected to its sports program. Most famously known for their Men's Division 1 Basketball and Football teams, as of 2020, Duke makes an estimated \$33,382,946 and \$39,669,829 in revenue, respectively (https://blackinblue.trinity.duke.edu/haves-and-have-nots-inequities-amongst-duke-universitys-sports-teams). Furthermore, Duke spends approximately \$1,329,949 per Men's basketball player and \$217,047 per football player (Ibid.). Duke's 2020 Equity in Athletics Disclosure Act (EADA) revealed that Duke spent a total of \$57,114,331 on men's sports teams and a total of \$25,472,405 on women's sports teams (Ibid.) This figure includes recruitment cost, amongst other things. This begs the question: is this the status quo in collegiate athletics?

**Context**

Duke University is intrinsically connected to its sports program. Most famously known for their Men's Division 1 Basketball and Football teams, as of 2020, Duke makes an estimated \$33,382,946 and \$39,669,829 in revenue, respectively (https://blackinblue.trinity.duke.edu/haves-and-have-nots-inequities-amongst-duke-universitys-sports-teams). Furthermore, Duke spends approximately \$1,329,949 per Men's basketball player and \$217,047 per football player (Ibid.). Duke's 2020 Equity in Athletics Disclosure Act (EADA) revealed that Duke spent a total of \$57,114,331 on men's sports teams and a total of \$25,472,405 on women's sports teams (Ibid.) This figure includes recruitment cost, amongst other things. This begs the question: is this the status quo in collegiate athletics?

**Explanation of Topic**

Our topic will specifically observe and investigate how much, on average, universities spend on recruitment. We will create a model that predicts this figure, based on the current a university's expenditure on athletic scholarships for student athletes. We will break down a number of variables within the data, looking at whether the institution is public versus private, has a football program or not, and what athletic division it falls under (I, II, or III). Our research question is: To what extent can college athletics' recruitment funds be predicted by the level of athletic scholarships provided to student athletes? We hypothesize that the ratio will, to a high degree, predict the recruitment funding --- as schools who allocate more money into students' financial aid will be willing to designate more money for their recruitment.

**Ethical Issues**

There are very few ethical issues anticipated with this investigation. However, it is important to note that source biases are an likely phenomenon. We must be careful with many self-reported information from university sites, and assuring that the data published can be verified.

**Methodology**

Research question: To what extent can college athletics' recruitment funds be predicted by the level of athletic scholarships provided to student athletes?

-   Private vs. public

-   Football vs. no football

-   Division

```{r}
#| label: filter-ncaa

eada_NCAA <- eada |>
  filter(classification_name == c("NCAA Division I-FCS", 
                                  "NCAA Division I-FBS", 
                                  "NCAA Division I without football", 
                                  "NCAA Division II with football", 
                                  "NCAA Division II without football", 
                                  "NCAA Division III with football", 
                                  "NCAA Division III without football",
                                  ""))
```

```{r}
#| label: filter-private

eada_private <- eada |>
  filter(sector_name == c("Private nonprofit, 4-year or above", 
         "Private for-profit, 4-year or above"))
```

```{r}
#| label: filter-public

eada_public <- eada |>
  filter(sector_name == c("Public, 4-year or above", "Public, 2-year"))
```

```{r}
#| label: filter-nofootball

eada_nofootball <- eada |>
  filter(classification_name == c("NCAA Division I without football", 
                                  "NCAA Division II without football", 
                                  "NCAA Division III without football"))
```

```{r}
#| label: filter-football

eada_football <- eada |>
  filter(classification_name != c("NCAA Division I without football", 
                                  "NCAA Division II without football", 
                                  "NCAA Division III without football"))
```

```{r}
#| label: filter-divisionI

eada_divisionI <- eada |>
  filter(classification_name == c("NCAA Division I-FCS",
                                  "NCAA Division I-FBS",
                                  "NCAA Division I without football"))
```

```{r}
#| label: filter-divisionII

eada_divisionII <- eada |>
  filter(classification_name == c("NCAA Division II with football",
                                  "NCAA Division II without football"))
```

```{r}
#| label: filter-divisionIII

eada_divisionIII <- eada |>
  filter(classification_name == c("NCAA Division III with football",
                                  "NCAA Division III without football"))
```

