---
title: "Project title"
subtitle: "Report"
format: html
editor: visual
execute:
  echo: true
---

```{r}
#| label: load-pkgs


library(tidyverse)
library(tidymodels)
```

```{r}
#| label: load-data

EADA_2021 = read.csv("data/Copy of EADA_2021.csv")


eada <- EADA_2021[,-27:-4274]
eada <- eada |> 
  mutate(ratio_mw_sa = STUAID_MEN_RATIO/STUAID_WOMEN_RATIO)
eada <- eada |>
  mutate(ratio_mw_ep = RECRUITEXP_MEN/RECRUITEXP_WOMEN)
eada <- eada |>
  filter(ratio_mw_sa != "NaN",
         ratio_mw_ep != "NaN",
         ratio_mw_sa != "Inf",
         ratio_mw_ep != "Inf")
glimpse(eada)
```

**Introduction**

**Context**

Duke University is intrinsically connected to its sports program. Most famously known for their Men's Division 1 Basketball and Football teams, as of 2020, Duke makes an estimated \$33,382,946 and \$39,669,829 in revenue, respectively (Laster, Jordan, et al. "The Haves and the Have-Nots: Inequities Amongst Duke University's Sports Teams." The Haves and the Have-Nots: Inequities Amongst Duke University's Sports Teams \| Black In Blue, 2020, https://blackinblue.trinity.duke.edu/haves-and-have-nots-inequities-amongst-duke-universitys-sports-teams.). Furthermore, Duke spends approximately \$1,329,949 per Men's basketball player and \$217,047 per football player (Ibid.). Duke's 2020 Equity in Athletics Disclosure Act (EADA) revealed that Duke spent a total of \$57,114,331 on men's sports teams and a total of \$25,472,405 on women's sports teams (Ibid.) This figure includes recruitment cost, amongst other things. Nationwide, there is a recorded inequity between NCAA sports (Meredith, L. (2017, June 21). NCAA Title IX Report: Spending up, gender gaps remain. The Seattle Times. https://www.seattletimes.com/sports/ncaa-title-ix-report-spending-up-gender-gaps-remain/). As Duke students, we were curious: is this the status quo in collegiate athletics?

**The Dataset**

The dataset we use to explore this topic comes from the U.S. Department of Education's Equity in Athletics Disclosure Act, which requires many schools to provide information regarding financial expenditure and revenue generation of their athletics departments. The dataset spans 4274 variables, including school names, locations, and cost breakdowns. There are 1844 observations in this dataset; each observation is a different school. The most recently published dataset is from 2021, which is the dataset we use.

**Explanation of Topic**

Our topic will specifically observe and investigate how much, on average, universities spend on recruitment. We will create a model that predicts this figure, based on the current a university's expenditure on athletic scholarships for student athletes. We will break down a number of variables within the data, looking at whether the institution is public versus private, has a football program or not, and what athletic division it falls under (I, II, or III). Our research question is: To what extent can college athletics' recruitment funds be predicted by the level of athletic scholarships provided to student athletes? We hypothesize that the ratio will, to a high degree, predict the recruitment funding --- as schools who allocate more money into students' financial aid will be willing to designate more money for their recruitment.

**Ethical Issues**

There are very few ethical issues anticipated with this investigation. However, it is important to note that source biases are a likely phenomenon. We must be careful with many self-reported information from university sites, and assuring that the data published can be verified.

**Methodology**

Research question: To what extent can college athletics' recruitment funds be predicted by the level of athletic scholarships provided to student athletes?

-   Private vs. public

-   Football vs. no football

-   Division

We will answer our research question by first creating subsets of our data by the factors listed above, and removing any outliers using the interquartile range rule. Then we create regression models comparing athletic scholarships to recruitment funds, and then calculate the AIC for each model to determine the effectiveness of each predictor. We chose to use regression models because our research question looks at the extent to which one variable can predict another. We chose to use AIC calculations because we are comparing the effectiveness of prediction based on which variables are included in the model, and AIC is an effective calculation for comparing models that is not simply dependent on the number of predictors.

```{r}
#| label: filter-ncaa

eada_NCAA <- eada |>
  filter(classification_name == "NCAA Division I-FCS" | 
        classification_name == "NCAA Division I-FBS" | 
        classification_name == "NCAA Division I without football" |
        classification_name == "NCAA Division II with football" |
        classification_name == "NCAA Division II without football" | 
        classification_name == "NCAA Division III with football" |
        classification_name == "NCAA Division III without football")


Q1_NCAA_ep <- quantile(eada_NCAA$ratio_mw_ep, .25)
Q1_NCAA_sa <- quantile(eada_NCAA$ratio_mw_sa, .25)

Q3_NCAA_ep <- quantile(eada_NCAA$ratio_mw_ep, .75)
Q3_NCAA_sa <- quantile(eada_NCAA$ratio_mw_sa, .75)

IQR_NCAA_ep <- IQR(eada_NCAA$ratio_mw_ep)
IQR_NCAA_sa <- IQR(eada_NCAA$ratio_mw_sa)

eada_NCAA <- subset(eada_NCAA, eada_NCAA$ratio_mw_ep> (Q1_NCAA_ep - 1.5*IQR_NCAA_ep) & eada_NCAA$ratio_mw_ep< (Q3_NCAA_ep + 1.5*IQR_NCAA_ep))

eada_NCAA <- subset(eada_NCAA, eada_NCAA$ratio_mw_sa> (Q1_NCAA_sa - 1.5*IQR_NCAA_sa) & eada_NCAA$ratio_mw_sa< (Q3_NCAA_sa + 1.5*IQR_NCAA_sa))
```

```{r}
#| label: filter-private

eada_private <- eada_NCAA |>
  filter(sector_name == "Private nonprofit, 4-year or above" | 
         sector_name == "Private for-profit, 4-year or above")



Q1_priv_ep <- quantile(eada_private$ratio_mw_ep, .25)
Q1_priv_sa <- quantile(eada_private$ratio_mw_sa, .25)

Q3_priv_ep <- quantile(eada_private$ratio_mw_ep, .75)
Q3_priv_sa <- quantile(eada_private$ratio_mw_sa, .75)

IQR_priv_ep <- IQR(eada_private$ratio_mw_ep)
IQR_priv_sa <- IQR(eada_private$ratio_mw_sa)

eada_private <- subset(eada_private, eada_private$ratio_mw_ep> (Q1_priv_ep - 1.5*IQR_priv_ep) & eada_private$ratio_mw_ep< (Q3_priv_ep + 1.5*IQR_priv_ep))

eada_private <- subset(eada_private, eada_private$ratio_mw_sa> (Q1_priv_sa - 1.5*IQR_priv_sa) & eada_private$ratio_mw_sa< (Q3_priv_sa + 1.5*IQR_priv_sa))
```

```{r}
#| label: filter-public

eada_public <- eada_NCAA |>
  filter(sector_name == "Public, 4-year or above" | 
         sector_name == "Public, 2-year")

Q1_public_ep <- quantile(eada_public$ratio_mw_ep, .25)
Q1_public_sa <- quantile(eada_public$ratio_mw_sa, .25)

Q3_public_ep <- quantile(eada_public$ratio_mw_ep, .75)
Q3_public_sa <- quantile(eada_public$ratio_mw_sa, .75)

IQR_public_ep <- IQR(eada_public$ratio_mw_ep)
IQR_public_sa <- IQR(eada_public$ratio_mw_sa)

eada_public <- subset(eada_public, eada_public$ratio_mw_ep> (Q1_public_ep - 1.5*IQR_public_ep) & eada_public$ratio_mw_ep< (Q3_public_ep + 1.5*IQR_public_ep))

eada_public <- subset(eada_public, eada_public$ratio_mw_sa> (Q1_public_sa - 1.5*IQR_public_sa) & eada_public$ratio_mw_sa< (Q3_public_sa + 1.5*IQR_public_sa))
```

```{r}
#| label: filter-nofootball

eada_nofootball <- eada |>
  filter(classification_name == "NCAA Division I without football" |
        classification_name == "NCAA Division II without football" | 
        classification_name == "NCAA Division III without football")

Q1_nofootball_ep <- quantile(eada_nofootball$ratio_mw_ep, .25)
Q1_nofootball_sa <- quantile(eada_nofootball$ratio_mw_sa, .25)

Q3_nofootball_ep <- quantile(eada_nofootball$ratio_mw_ep, .75)
Q3_nofootball_sa <- quantile(eada_nofootball$ratio_mw_sa, .75)

IQR_nofootball_ep <- IQR(eada_nofootball$ratio_mw_ep)
IQR_nofootball_sa <- IQR(eada_nofootball$ratio_mw_sa)

eada_nofootball <- subset(eada_nofootball, eada_nofootball$ratio_mw_ep> (Q1_nofootball_ep - 1.5*IQR_nofootball_ep) & eada_nofootball$ratio_mw_ep< (Q3_nofootball_ep + 1.5*IQR_nofootball_ep))

eada_nofootball <- subset(eada_nofootball, eada_nofootball$ratio_mw_sa> (Q1_nofootball_sa - 1.5*IQR_nofootball_sa) & eada_nofootball$ratio_mw_sa< (Q3_nofootball_sa + 1.5*IQR_nofootball_sa))
```

```{r}
#| label: filter-football

eada_football <- eada |>
  filter(classification_name != "NCAA Division I without football" | 
         classification_name != "NCAA Division II without football" | 
         classification_name != "NCAA Division III without football")

Q1_football_ep <- quantile(eada_football$ratio_mw_ep, .25)
Q1_football_sa <- quantile(eada_football$ratio_mw_sa, .25)

Q3_football_ep <- quantile(eada_football$ratio_mw_ep, .75)
Q3_football_sa <- quantile(eada_football$ratio_mw_sa, .75)

IQR_football_ep <- IQR(eada_football$ratio_mw_ep)
IQR_football_sa <- IQR(eada_football$ratio_mw_sa)

eada_football <- subset(eada_football, eada_football$ratio_mw_ep> (Q1_football_ep - 1.5*IQR_football_ep) & eada_football$ratio_mw_ep< (Q3_football_ep + 1.5*IQR_football_ep))

eada_football <- subset(eada_football, eada_football$ratio_mw_sa> (Q1_football_sa - 1.5*IQR_football_sa) & eada_football$ratio_mw_sa< (Q3_football_sa + 1.5*IQR_football_sa))
```

```{r}
#| label: filter-divisionI

eada_divisionI <- eada |>
  filter(classification_name == "NCAA Division I-FCS" |
         classification_name == "NCAA Division I-FBS" |
         classification_name == "NCAA Division I without football")


Q1_divisionI_ep <- quantile(eada_divisionI$ratio_mw_ep, .25)
Q1_divisionI_sa <- quantile(eada_divisionI$ratio_mw_sa, .25)

Q3_divisionI_ep <- quantile(eada_divisionI$ratio_mw_ep, .75)
Q3_divisionI_sa <- quantile(eada_divisionI$ratio_mw_sa, .75)

IQR_divisionI_ep <- IQR(eada_divisionI$ratio_mw_ep)
IQR_divisionI_sa <- IQR(eada_divisionI$ratio_mw_sa)

eada_divisionI <- subset(eada_divisionI, eada_divisionI$ratio_mw_ep> (Q1_divisionI_ep - 1.5*IQR_divisionI_ep) & eada_divisionI$ratio_mw_ep< (Q3_divisionI_ep + 1.5*IQR_divisionI_ep))

eada_divisionI <- subset(eada_divisionI, eada_divisionI$ratio_mw_sa> (Q1_divisionI_sa - 1.5*IQR_divisionI_sa) & eada_divisionI$ratio_mw_sa< (Q3_divisionI_sa + 1.5*IQR_divisionI_sa))
```

```{r}
#| label: filter-divisionII

eada_divisionII <- eada |>
  filter(classification_name == "NCAA Division II with football" |
        classification_name == "NCAA Division II without football")

Q1_divisionII_ep <- quantile(eada_divisionII$ratio_mw_ep, .25)
Q1_divisionII_sa <- quantile(eada_divisionII$ratio_mw_sa, .25)

Q3_divisionII_ep <- quantile(eada_divisionII$ratio_mw_ep, .75)
Q3_divisionII_sa <- quantile(eada_divisionII$ratio_mw_sa, .75)

IQR_divisionII_ep <- IQR(eada_divisionII$ratio_mw_ep)
IQR_divisionII_sa <- IQR(eada_divisionII$ratio_mw_sa)

eada_divisionII <- subset(eada_divisionII, eada_divisionII$ratio_mw_ep> (Q1_divisionII_ep - 1.5*IQR_divisionII_ep) & eada_divisionII$ratio_mw_ep< (Q3_divisionII_ep + 1.5*IQR_divisionII_ep))

eada_divisionII <- subset(eada_divisionII, eada_divisionII$ratio_mw_sa> (Q1_divisionII_sa - 1.5*IQR_divisionII_sa) & eada_divisionII$ratio_mw_sa< (Q3_divisionII_sa + 1.5*IQR_divisionII_sa))
```

```{r}
#| label: filter-divisionIII

eada_divisionIII <- eada |>
  filter(classification_name == "NCAA Division III with football" |
         classification_name == "NCAA Division III without football")

Q1_divisionIII_ep <- quantile(eada_divisionIII$ratio_mw_ep, .25)
Q1_divisionIII_sa <- quantile(eada_divisionIII$ratio_mw_sa, .25)

Q3_divisionIII_ep <- quantile(eada_divisionIII$ratio_mw_ep, .75)
Q3_divisionIII_sa <- quantile(eada_divisionIII$ratio_mw_sa, .75)

IQR_divisionIII_ep <- IQR(eada_divisionIII$ratio_mw_ep)
IQR_divisionIII_sa <- IQR(eada_divisionIII$ratio_mw_sa)

eada_divisionIII <- subset(eada_divisionIII, eada_divisionIII$ratio_mw_ep> (Q1_divisionIII_ep - 1.5*IQR_divisionIII_ep) & eada_divisionIII$ratio_mw_ep< (Q3_divisionIII_ep + 1.5*IQR_divisionIII_ep))

eada_divisionIII <- subset(eada_divisionIII, eada_divisionIII$ratio_mw_sa> (Q1_divisionIII_sa - 1.5*IQR_divisionIII_sa) & eada_divisionIII$ratio_mw_sa< (Q3_divisionIII_sa + 1.5*IQR_divisionIII_sa))
```

```{r}
#| label: main-visualization

eada |>
  ggplot(
    aes(x = ratio_mw_sa,
        y = ratio_mw_ep)
  ) + 
  geom_point() + 
  geom_smooth(method = "lm") +
  labs(x = "Ratio of Student Aid of Men to Women", 
       y = "Ratio of Recruiting Expenditures of Men to Women",
       title = "Relationship between Student Aid and Recruting Expenditures",
       subtitle = "Ratios of Men to Women")
```

```{r}
#| label: AIC-main
linear_reg() |>
  set_engine("lm") |>
  fit(ratio_mw_ep ~ ratio_mw_sa, data = eada) |>
  glance() |>
  pull(AIC, r.squared)
```

While filtering our data sets, we made the decision to remove outliers using the formula (1st Quadrant - 1.5(IQR)), (3rd Quadrant + 1.5(IQR)). While originally analyzing our data, the outliers strongly influenced what seemed like an exponential model. As a result, we decided to take out the outliers and calculate a linear model to examine how strongly the male to female ratio of student aid is related to the male to female ratio of recruiting expenditures. Below is the change in our plot and linear model fit.

```{r}
#| label: viz-no-outs
Q1_no_outs_ep <- quantile(eada$ratio_mw_ep, .25)
Q1_no_outs_sa <- quantile(eada$ratio_mw_sa, .25)

Q3_no_outs_ep <- quantile(eada$ratio_mw_ep, .75)
Q3_no_outs_sa <- quantile(eada$ratio_mw_sa, .75)

IQR_no_outs_ep <- IQR(eada$ratio_mw_ep)
IQR_no_outs_sa <- IQR(eada$ratio_mw_sa)

eada_no_outs <- subset(eada, eada$ratio_mw_ep> (Q1_no_outs_ep - 1.5*IQR_no_outs_ep) & eada$ratio_mw_ep< (Q3_no_outs_ep + 1.5*IQR_no_outs_ep))

eada_no_outs <- subset(eada, eada$ratio_mw_sa> (Q1_no_outs_sa - 1.5*IQR_no_outs_sa) & eada$ratio_mw_sa< (Q3_no_outs_sa + 1.5*IQR_no_outs_sa))

eada_no_outs |>
  ggplot(
    aes(x = ratio_mw_sa,
        y = ratio_mw_ep)) + 
  geom_point() + geom_smooth(method = "lm") +
  labs(x = "Ratio of Student Aid of Men to Women", 
       y = "Ratio of Recruiting Expenditures of Men to Women",
       title = "Relationship between Student Aid and Recruting Expenditures",
       subtitle = "Outliers taken out")

```

```{r}
#| label: aic-no-outs
linear_reg() |>
  set_engine("lm") |>
  fit(ratio_mw_ep ~ ratio_mw_sa, data = eada_no_outs) |>
  glance() |>
  pull(AIC, r.squared)
```

Private vs. public schools have two very different financial structures, so we thought there may be a tangible difference in how the two ratios relate to each other. Below, we fit a linear model and calculated the AIC and r squared for each.

```{r}
#| label: viz-priv
eada_private |>
  ggplot(
    aes(x = ratio_mw_sa,
        y = ratio_mw_ep)) + 
  geom_point() + geom_smooth(method = "lm") +
   labs(x = "Ratio of Student Aid of Men to Women", 
       y = "Ratio of Recruiting Expenditures of Men to Women",
       title = "Relationship between Student Aid and Recruting Expenditures",
       subtitle = "Private Schools")

```

```{r}
#| label: AIC-priv
linear_reg() |>
  set_engine("lm") |>
  fit(ratio_mw_ep ~ ratio_mw_sa, data = eada_private) |>
  glance() |>
  pull(AIC, r.squared)

```

```{r}
#| label: viz-public
eada_public |>
  ggplot(
    aes(x = ratio_mw_sa,
        y = ratio_mw_ep)
  ) + geom_point() + geom_smooth(method = "lm") +
 labs(x = "Ratio of Student Aid of Men to Women", 
       y = "Ratio of Recruiting Expenditures of Men to Women",
       title = "Relationship between Student Aid and Recruting Expenditures",
       subtitle = "Public Schools")
```

```{r}
#| label: AIC-public
linear_reg() |>
  set_engine("lm") |>
  fit(ratio_mw_ep ~ ratio_mw_sa, data = eada_public) |>
  glance() |>
  pull(AIC, r.squared)
```

For most collegiate athletic programs in the United States, football serves as the primary source of revenue. As a result, we decided to look at how the inclusion or absence of football impacted the fit of the linear model. Below, there's the AIC and r squared calculated for each.

```{r}
#| label: viz-football
eada_football |>
  ggplot(
    aes(x = ratio_mw_sa,
        y = ratio_mw_ep)
  ) + geom_point() + geom_smooth(method = "lm") +
   labs(x = "Ratio of Student Aid of Men to Women", 
       y = "Ratio of Recruiting Expenditures of Men to Women",
       title = "Relationship between Student Aid and Recruting Expenditures",
       subtitle = "Schools with football")
```

```{r}
#| label: AIC-football
linear_reg() |>
  set_engine("lm") |>
  fit(ratio_mw_ep ~ ratio_mw_sa, data = eada_football) |>
  glance() |>
  pull(AIC, r.squared)
  
```

```{r}
#| label: viz-no-football
eada_nofootball |>
  ggplot(
    aes(x = ratio_mw_sa,
        y = ratio_mw_ep)
  ) + geom_point() + geom_smooth(method = "lm") +
   labs(x = "Ratio of Student Aid of Men to Women", 
       y = "Ratio of Recruiting Expenditures of Men to Women",
       title = "Relationship between Student Aid and Recruting Expenditures",
       subtitle = "Schools with no football")
```

```{r}
#| label: AIC-no-football
linear_reg() |>
  set_engine("lm") |>
  fit(ratio_mw_ep ~ ratio_mw_sa, data = eada_nofootball) |>
  glance() |>
  pull(AIC, r.squared)
```

Finally, as the level of competition increases, so does the level of finances. With that being said, we split the data into three categories by division and looked at how it impacted a linear model fit. The AIC and r squared values are calculated below for each.

```{r}
#| label: viz-d1
eada_divisionI |>
  ggplot(
    aes(x = ratio_mw_sa,
        y = ratio_mw_ep)
  ) + geom_point() + geom_smooth(method = "lm") +
   labs(x = "Ratio of Student Aid of Men to Women", 
       y = "Ratio of Recruiting Expenditures of Men to Women",
       title = "Relationship between Student Aid and Recruting Expenditures",
       subtitle = "Division I schools")
```

```{r}
#| label: AIC-d1
linear_reg() |>
  set_engine("lm") |>
  fit(ratio_mw_ep ~ ratio_mw_sa, data = eada_divisionI) |>
  glance() |>
  pull(AIC, r.squared)
```

```{r}
#| label: viz-d2
eada_divisionII |>
  ggplot(
    aes(x = ratio_mw_sa,
        y = ratio_mw_ep)
  ) + geom_point() + geom_smooth(method = "lm") +
   labs(x = "Ratio of Student Aid of Men to Women", 
       y = "Ratio of Recruiting Expenditures of Men to Women",
       title = "Relationship between Student Aid and Recruting Expenditures",
       subtitle = "Division II schools")
```

```{r}
#| label: AIC-d2
linear_reg() |>
  set_engine("lm") |>
  fit(ratio_mw_ep ~ ratio_mw_sa, data = eada_divisionII) |>
  glance() |>
  pull(AIC, r.squared)
```

```{r}
#| label: viz-d3
eada_divisionIII |>
  ggplot(
    aes(x = ratio_mw_sa,
        y = ratio_mw_ep)
  ) + geom_point() + geom_smooth(method = "lm") +
   labs(x = "Ratio of Student Aid of Men to Women", 
       y = "Ratio of Recruiting Expenditures of Men to Women",
       title = "Relationship between Student Aid and Recruting Expenditures",
       subtitle = "Division III schools")

```

```{r}
#| label: AIC-d3
linear_reg() |>
  set_engine("lm") |>
  fit(ratio_mw_ep ~ ratio_mw_sa, data = eada_divisionIII) |>
  glance() |>
  pull(AIC, r.squared)
```

To more fully answer our research question, we created a multivariate prediction model to reach conclusions about the factors that influence the male to female ratio of recruitment funds. Below, we wrangled our data set to create three new variables, school_type(private or public), football(football or no football), and division (one, two, or three). Then, we fit our multivariate prediction model.

```{r}
#| label: datawrangle-model

eada_wrangled <- eada_no_outs |>
  mutate(division = case_when(
    classification_name == "NCAA Division I-FCS" ~ "one",
    classification_name == "NCAA Division I-FBS" ~ "one",
    classification_name == "NCAA Division I without football" ~ "one",
    classification_name == "NCAA Division II with football" ~ "two",
    classification_name == "NCAA Division II without football" ~ "two",
    classification_name == "NCAA Division III without football" ~ "three",
    classification_name == "NCAA Division III without football" ~ "three")) |>
  mutate(football = case_when(
    classification_name == "NCAA Division I without football" ~ "no football",
    classification_name == "NCAA Division II without football" ~ "no football",
    classification_name == "NCAA Division III without football" ~ "no football",
    classification_name == "NCAA Division I-FCS" ~ "football",
    classification_name == "NCAA Division I-FBS" ~ "football",
    classification_name == "NCAA Division II with football" ~ "football", 
    classification_name == "NCAA Division III with football" ~ "football")) |>
  mutate(school_type = case_when(
    sector_name == "Public, 4-year or above" ~ "public",
    sector_name == "Public, 2-year" ~ "public",
    sector_name == "Private nonprofit, 4-year or above" ~ "private", 
    sector_name == "Private for-profit, 4-year or above" ~ "private"))
```

```{r}
model <- linear_reg() |>
  set_engine("lm") |>
  fit(ratio_mw_ep ~ school_type + division + football + ratio_mw_sa, 
      data = eada_wrangled) |>
  tidy()
```

$\hat{ratio\_mw\_ep} = 3.688 -0.651({school\_type}) - 0.829({division\_three}) - .848({division\_two}) - 1.592({no\_football}) + 0.086({ratio\_mw\_sa})$

Our model predicts that private, division one football schools have the highest ratio of male to female recruitment funds. Further, whether a school has football holds the highest weight as an influencing factor. Further, the model displays that there is a slight positive correlation between a higher male to female student aid ratio and a higher male to female recruitment fund ratio.

**Results**

This prediction model was aimed at testing whether the financial allocation universities spent on athletic scholarship could predict the amount they allocated for recruitment. We filtered the data through three different variables: whether the school had a football program or not, whether the school was public or private, and whether the school was Division I, II, or III. Notably, many of these groups did not have equal numbers of schools, and division 3 is only 9 schools.

It is important to note the biases that may have effected the data outcome. Division III schools do not allocate any money towards athletic scholarships. Furthermore, financial capabilities widely vary between public and private schools, as well as, how much income the school makes from their athletic programs.

After filtering the data, we ran an AIC metric on all the subsets of the data to compare the different regression models. There was a more accurate trend observed in the private vs. public data-set, meaning that model offers the best fit. Amongst all the graphs, there is a low positive correlation observed. Then we ran an R squared test. This would tell us the significance in the correlation between the two variables: scholarship funds versus recruitment funds. The R squared test revealed that there is a very insignificant correlation between the two chosen variables.

|                     |                           |                                            |                               |                              |
|---------------|---------------|---------------|---------------|---------------|
| [Data:]{.underline} | [All Schools]{.underline} | [All Schools Outliers Removed]{.underline} | [Private Schools]{.underline} | [Public Schools]{.underline} |
| AIC:                | 7723.431                  | 7409.35                                    | 490.849                       | 869.687                      |
| R Square:           | 0.008                     | 0.003                                      | 0.112                         | 0.082                        |

|                     |                                |                                   |                          |                           |                            |
|------------|------------|------------|------------|------------|------------|
| [Data:]{.underline} | [Football Schools]{.underline} | [No Football Schools]{.underline} | [DI Schools]{.underline} | [DII Schools]{.underline} | [DIII Schools]{.underline} |
| AIC:                | 2484.094                       | 374.648                           | 1167.375                 | 554.459                   | -1.120                     |
| R Square:           | 0.079                          | 0.025                             | 0.103                    | 0.127                     | 0.039                      |

Without filtering the data at all and not faceting the data by any groups, there is a 0.008 correlation between the two variables. This shows that it is incredibly low positive correlation. Additionally, There is an AIC of 7723.431. After filtering the data and removing outliers, we see that the AIC decreased, indicating that removing the outliers reduced the variability in the data, and that the data was better fit after removing outliers.

Something about a negative AIC?? Something about low correlation.
